Supplement to Initial estuarine response to the nutrient-rich Piney Point release into Tampa Bay, Florida

### 2021-12-07 manu-draft.Rmd
added knb links

The R statistical programming language (v4.0.2) was used for all analyses [@RCT20].  We imported data using the googlesheets4 [@Bryan20] and googledrive [@DAgostino20] R packages and used tidyverse [@Wickham19] packages to format data for analysis.  The tbeptools R package [@Beck21] was used to import and summarize long-term monitoring data (EPC water quality data and seagrass transect data). The NADA R package [@Lee20] was used for analysis of censored data. All spatial analyses were done using the simple features (sf) R package [@Pebesma18]. The mgcv R package [@Wood17] was used to create the GAMs for water quality parameters.

All datasets used in this study are available from an open access data archive hosted on the Knowledge Network for Biocomplexity.  Materials for reproducing the analyses, figures, tables, and other content in this paper are provided in a GitHub repository. Finally, the Piney Point Environmental Monitoring Dashboard can be used to view all data included in this paper through an interactive, online application.  Links and details are provided in supplement.

>>>>

The R statistical programming language (v4.0.2) was used for all analyses [@RCT20].  We imported data using the googlesheets4 [@Bryan20] and googledrive [@DAgostino20] R packages and used tidyverse [@Wickham19] packages to format data for analysis.  The tbeptools R package [@Beck21] was used to import and summarize long-term monitoring data (EPC water quality data and seagrass transect data). The NADA R package [@Lee20] was used for analysis of censored data. All spatial analyses were done using the simple features (sf) R package [@Pebesma18]. The mgcv R package [@Wood17] was used to create the GAMs for water quality parameters. All datasets used in this study are available from an open access data archive hosted on the Knowledge Network for Biocomplexity [@Beck21d].  Materials for reproducing the analyses, figures, tables, and other content in this paper are provided in a GitHub repository. Finally, the Piney Point Environmental Monitoring Dashboard can be used to view all data included in this paper through an interactive, online application [@Beck21c].  Links and details are provided in supplement.

### 2021-12-07 supplement.Rmd
added knb links

All datasets used in this study are provided online in an open access data archive hosted on the Knowledge Network for Biocomplexity as part of the DataOne federated network.  This includes full metadata documentation.  The repository is available and citable at:

@@

The Piney Point Environmental Monitoring Dashboard can be used to view all data together through an interactive, online application.  It provides a synthesis of data to assess baseline conditions prior to April 2021 and to evaluate changing water quality conditions as new data become available. The dashboard is available at https://shiny.tbep.org and citable at @Beck21c.

>>>>

All datasets used in this study are provided online in an open access data archive hosted on the Knowledge Network for Biocomplexity as part of the DataOne federated network.  This includes full metadata documentation.  The repository is available at https://knb.ecoinformatics.org/view/doi:10.5063/F1959G05 and citable as @Beck21d.

@@

The Piney Point Environmental Monitoring Dashboard can be used to view all data together through an interactive, online application.  It provides a synthesis of data to assess baseline conditions prior to April 2021 and all 2021 monitoring data collected in response to the Piney Point event. The dashboard is available at https://shiny.tbep.org and citable as @Beck21c.
